\textbf{Parallel dragonfly algorithm} \\[2ex] \large High Performance Computing for Data Science course 2024/2025

### 2025-08-27 text-paper/paper.tex
small changes

After the end of all tasks it is possible to check how much gain in performance we have obtained.
To do this it is necessary to introduce some theoretical concepts that will give us the tools that
will give us a good metric system to evaluate our results.Speedup is defined as the ratio between the the execution times of the serial and parallel
implementations, so the formula will be equal to: $$Speedup = \frac{T_{serial}}{T_{parallel}}$$ 
from this definition it is obvious that the more the speedup is the more the parallel implementation
performs better. There is a particular case where the time execution of the denominator can be defined
as $T_{parallel}=T_{serial}/p$, where \textit{p} is the number of cores: this is called \textit{linear speedup},
and in this situation it perfectly match with the classic speedup coefficient
Efficiency is another important parameter, and it is defined by the ratio of the speedup and the 
number of cores, giving the following formula: $$E = \frac{Speedup}{p}$$
also in this case the efficiency decrease due to the increase of the number of cores. In case
of linear speedup we get that the efficiency is equal to the inverse of $p$
\subsection*{results}
\label{results}
Now it is possible to show results obtained from the cluster,
using the configuration with 4 cores and 1 thread will be considered
equal as the serial time
\newline

>>>>

After the end of all tasks it is possible to check how much gain in performance we have obtained.
To do this it is necessary to introduce some theoretical concepts that will give us the tools that
will give us a good metric system to evaluate our results.Speedup is defined as the ratio between the the execution times of the serial and parallel
implementations, so the formula will be equal to: $$Speedup = \frac{T_{serial}}{T_{parallel}}$$ 
from this definition it is obvious that the more the speedup is the more the parallel implementation
performs better. There is a particular case where the time execution of the denominator can be defined
as $T_{parallel}=T_{serial}/p$, where \textit{p} is the number of cores: this is called \textit{linear speedup},
and in this situation it perfectly match with the classic speedup coefficient
Efficiency is another important parameter, and it is defined by the ratio of the speedup and the 
number of cores, giving the following formula: $$E = \frac{Speedup}{p}$$
also in this case the efficiency decrease due to the increase of the number of cores. In case
of linear speedup we get that the efficiency is equal to the inverse of $p$
\subsection*{results}
\label{results}
Now it is possible to show results obtained from the cluster,
using the configuration with 4 cores and 1 thread will be considered
equal as the serial time. The reason for this approach is that a single core computation would require 1024 times the workload of the 1024 process version, but we calibrated the 1024 core version to take 3 minutes.
